---
title       : Predicting AFL Team Performance
subtitle    : The James Hird Memerial Ladder Predictor
author      : J Burgess
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : zenburn      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Australian Rules Football (AFL)
* Australian Field Sport
* Popular in the south-East States
* Kick a ball through the goals to win

--- .class #id 

## Measures of Performance

Some Teams are much better than others
* Hawthorn are great!
* Melbourne, not so much

Let's look at some variables to include in our prediction function

--- .class #id


Kicking the ball through the middle posts

```{r,echo=FALSE}
setwd("~\\AFLScraper")
dataI<-read.csv("TeamstatsI.csv")
data<-dataI[,c(1,2,6,8)]#,3,4,5,9,13,12)]#,3,8,9)]

plot(dataI[,8],dataI[,1],main = 'AFL 2014', col=3+ (dataI$Rank > 8),ylab="Ladder Position",xlab="Goals")

```

--- .class #id


Successfully passing the ball

```{r,echo=FALSE}

plot(dataI[,6],dataI[,1],main = 'AFL 2014', col=3+ (dataI$Rank > 8),ylab="Ladder Position",xlab="Disposals")

```


